A Comparision of Bootstrap Methods

### 2022-11-30 project/PaperTemplate/paper.Rmd
Working on simulation

nboot <- 10000

@@

Justin,

An example before a simulation could be useful if your simulation is assessing their performance (i.e. if your simulation is like Hmk 8, where you do a lot of reps to check performance). You could run anything on an existing data set (the one we have from Hmk 4/5), for example, that you want. I think you have enough without worrying about the parametric bootstrap.

@@

mean.fun <- function(d, i) {
  d <- X[i]
  return (mean(d))
}

@@

ci <- boot.ci(results, type = "all")

@@

```{r}
set.seed(1)

for(i in 1: reps) {
  x <- rnorm(n, 40, 3)
  y <- rgamma(n, 8, 2)

```{r}
simbootstraps <- function(dataset, trueparameter) {

@@

}

simnormal <- function(locationinput, scaleinput, testcenterinput, ninput, repsinput = 1000){
# Set Useful Values
reps <- repsinput #number of repetitions
location <- locationinput 
scale <- scaleinput
testcenter <- testcenterinput #center to test for
n <- ninput #sample size

#Initialize storage vectors
tpvals <- rep(0,reps)
spvals <- rep(0,reps)
srpvals <- rep(0,reps)

#Generate random data, do tests, save p-values
for(i in 1:reps){
  x <- rnorm(n, location, scale)
  tpvals[i] <- t.test(~x, mu = testcenter)$p.value 
  spvals[i] <- SIGN.test(x, md = testcenter)$p.value 
  srpvals[i] <- wilcox.test(x, mu = testcenter)$p.value 
}

output <- c(sum(tpvals <= 0.05)/reps, sum(spvals <= 0.05)/reps, sum(srpvals <= 0.05)/reps)
names(output) <- c("Ttest", "Sign", "SignedRank")
output
}
```

>>>>

#nboot <- 10000

@@

@@

mean.fun <- function(d, i) {
  d <- X[i]
  return (c(mean(d), sd(d)))
}

@@

ci <- boot.ci(results, type = "all")
ci

@@

```{r}
findCIs <- function(sampleinput, trueparameter, nboot) {

  sample_mean <- mean(~ Dec, data = sampleinput)
  sample_sd <- sd(~ Dec, data = sampleinput)
  sample_n <- nrow(sampleinput)

  alphalow <- 0.025
  alphahigh <- 0.975

  #perform bootstrap
  mean <- rep(0,nboot)
  sd <- rep(0,nboot)
  se <- rep(0,nboot)
  t_stat <- rep(0,nboot)

  for (i in 1:nboot) {
    resampled <- as.data.frame(mosaic::resample(sampleinput, replace = TRUE))
    mean[i] <- mean(~ Dec, data = resampled)
    sd[i] <- sd(~ Dec, data = resampled)
    se[i] <- sd[i]/sqrt(nrow(resampled))
    t_stat[i] <- (mean[i] - orig_mean)/se[i]
  }

  boot_means <- as.data.frame(mean)
  boot_t_stat <- as.data.frame(t_stat)

  # find the standard confidence interval
  standard_interval <- sample_mean + qnorm(c(0.025, 0.975)) * sample_sd/sqrt(sample_n)

  # find percentile interval
  percentile_interval <- qdata(~ mean, c(0.025, 0.975), data = boot_means)

  # find BC interval
  less_than_sample_mean <- sum(ifelse(boot_means <= sample_mean, 1, 0))/nboot
  z0 <- qnorm(less_than_sample_mean)
  newlow <- pnorm(2*z0 + qnorm(alphalow))
  newhigh <- pnorm(2*z0 + qnorm(alphahigh))

  bc_interval <- qdata(~ mean, c(newlow, newhigh), data = boot_means)

  # find BCa interval
  theta <- function(x){mean(x)}
  jackknife_results <- bootstrap::jackknife(sampleinput$Dec, theta)
  jackmean <- mean(~ jackknife_results$jack.values)
  estimated_a <- (1/6)*sum((jackknife_results$jack.values - jackmean)^3)/
    (sum((jackknife_results$jack.values - jackmean)^2))^(1.5)
  a_newlow <- pnorm(z0 + (z0 + qnorm(alphalow))/(1-estimated_a*(z0 + qnorm(alphalow))))
  a_newhigh <- pnorm(z0 + (z0 + qnorm(alphahigh))/(1-estimated_a*(z0 + qnorm(alphahigh))))
  bca_interval <- qdata(~ mean, c(a_newlow, a_newhigh), data = boot_means)

  # find studentized
  q <- unname(quantile(boot_t_stat$t_stat, c(0.025, 0.975)))
  lower <- q[1]
  upper <- q[2]
  t_interval <- c(orig_mean - upper*orig_se, orig_mean - lower*orig_se)

  output <- c(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
  output
}

@@

OUTPUT1 <- findCIs(SnowGR, 0, 10)
```
